\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[blue]{classic} 
\usepackage[utf8]{inputenc}  %Windows 

%\usepackage[scale=0.975]{geometry}
\usepackage[top=0.5cm, bottom=0.5cm, left=0.5cm, right=0.5cm]{geometry}
\usepackage{graphicx}

\firstname{Vadim}
\familyname{Volodin}  
\mobile{+79528860485}    
\homepage{polyprogrammist.github.io}                
\email{pechkin350@gmail.com}                              
\social[github]{polyprogrammist}
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\usepackage{multibib}
\newcites{book,misc}{{Books},{Others}}

\nopagenumbers{} 

\begin{document}
\makecvtitle

%experience
%education
%technical experience 
%additional experience
%languages and technologies

\renewcommand*{\cventry}[7][.25em]{%
  \cvitem[#1]{#2}{%
    {\bfseries#3}%
%   \ifthenelse{\equal{#4}{}}{}{, {\slshape#4}}% I changed this line (with comma) ...
    \ifthenelse{\equal{#4}{}}{}{ {\slshape#4}}% ... into this one (without comma).
    \ifthenelse{\equal{#5}{}}{}{, #5}%
    \ifthenelse{\equal{#6}{}}{}{, #6}%
    .\strut%
    \ifx&#7&%
      \else{\newline{}\begin{minipage}[t]{\linewidth}\small#7\end{minipage}}\fi}}

\section{Experience}
\cventry{}{}{Micran, internship, summer 2018}{}{}{{}%
\begin{itemize}
\item Implemented the plugin for radar software using C++, Qt and linux. It was aimed to test radar engines.
\end{itemize}}
\cventry{}{}{Yandex, practice, spring 2018}{}{}{{}%
\begin{itemize}
\item Worked with ReactJS on the project Secret Santa.
\end{itemize}}

\section{Education}
\cventry{f}{g}{Saint Petersburg State University}{a}{a}{{c}%
\begin{itemize}
\item Worked with ReactJS on the project Secret Santa.
\end{itemize}}
\cventry{}{}{Saint Petersburg State University. Bachelor's in Software Engineering. 2016-2020}{}{}{}
\cventry{}{}{Computer Science Center. Software Engineering, Data Analysis. 2017-2020}{}{}{}

\section{Technical experience}
\cvitem{}{DirectoriesSynchronize - a tool to synchronize }

\section{Additional experience}
\cvitem{}{Reached division 1 on Codeforces}
\cvitem{}{Participated in 3 hackatons}

\section{Languages and Technologies}
\cvitem{}{C++, QT}
\cvitem{}{Java, spring}
\cvitem{}{Python, pyqt, django, scikit-learn, pandas, numpy}
\cvitem{}{C\#}
\cvitem{}{linux}
\cvitem{}{postgres}
\cvitem{}{JS, ReactJS}
\cvitem{}{HTML, CSS}
\cvitem{}{Lisp, Haskell, Paskal}

\end{document}
